C_exp_1

### 2018-08-31 experiments/A_pilot_1/writeup/A_pilot_1.Rmd
consistent YAML

This document aims to be a complete and up to date record of the analysis for vagueness 0, the pilot experiment.

The pilot experiment used subitizable numbers as well as bigger numbers.
The instructions had the form: _Choose the square with {{few, many},{two, three, four, five, six, seven, eight, nine}} dots._
The variables were: subitizability; vagueness; target_size; gap_size; side (i.e., which side was the bigger number on?)

# Libraries and functions

Load libraries.

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(dotwhisker)
library(grid)
library(gridExtra)
library(lme4)
# R CMD INSTALL broom.mixed # https://github.com/bbolker/broom.mixed
```

Source additional R files with functions for computing confidence intervals.

```{r sourceCIFunctions}
source("CIfunctions.R") # for summarySEwithin etc
```

# Data

Get the data.

```{r "make the data.txt file unless it's already there; read the data from file, add some vars and code the added vars", message=FALSE}

# make the data file from the individual subjects' data unless it's already there in the directory
if (!file.exists("data.txt")) {
  system("echo 'gap\ttarget\tside\tvagueness\tpair\tVersion\tLeft\tRight\tText\tCondition\tcorrectAnswer\tsubject\tactualAnswer\tisCorrect\trt' > data.txt")
  system("cat ../experimentCode/output/*.dat >> data.txt", wait=TRUE)
}

# read in the data from file
din <- read_delim("data.txt", delim="\t")

@@

```{r "make a tibble with factors explicit"}
# make a df to carry forward
d <- tibble(
  obs = din$obs, 
  trial = din$trial, 
  subject = as.factor(din$subject), 
  item = factor(din$pair, label = c("2:4", "3:5", "6:8", "7:9", "2:6", "7:3", "8:4", "5:9")),
  gap = factor(din$gap, levels = c("BigGap", "SmallGap"), labels = c("Big Gap", "Small Gap")), 
  quan = factor(din$target, levels = c("BigTarget", "SmallTarget"), labels = c("Big Target", "Small Target")), 
  vag = factor(din$vagueness, levels = c("Precise", "Vague"), labels = c("Crisp", "Vague")), 
  subit = factor(ifelse(din$pair %in% c(1,2,5,6), "Subitizable", "Not subitizable")),
  side = factor(din$side), 
  text = factor(din$Text),
  err = 1 - din$isCorrect, 
  rt_ms = din$rt,
  rt_log = log( din$rt ),
  rt_reciprocal = -1/din$rt # rate of slowing: # We multiplied reciprocal scores [1/RT] by -1 [-1/RT] to maintain the direction of effects compatible for the three variants, effectively converting speed [number of responses per ms] into 'rate of slowing' - A linear mixed model analysis of masked repetition priming, Kliegl, Masson & Richter, VISUAL COGNITION,2010,18(5),655--681 (p.~662) 
)
```

>>>>

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source('summarySEwithin2.R')
source("A_pilot_1_functions/pretty_coef_table.R")
```

The experiment used subitizable numbers as well as bigger numbers. The instructions had the form: _Choose the square with {{few, many},{two, three, four, five, six, seven, eight, nine}} dots._ The variables were: subitizability; vagueness; target_size; gap_size; side (i.e., which side was the bigger number on?)

```{r "read the data from file, add some vars", message=FALSE}
# read in the data from file
din <- read_delim("data.txt", delim="\t")

@@

```{r "make a tibble with factors explicit"}
# make a df to carry forward
d <- tibble(
  obs = din$obs, 
  trial = din$trial, 
  subject = as.factor(din$subject), 
  item = factor(din$pair, label = c("2:4", "3:5", "6:8", "7:9", "2:6", "7:3", "8:4", "5:9")),
  gap = factor(din$gap, levels = c("BigGap", "SmallGap"), labels = c("Big Gap", "Small Gap")), 
  quan = factor(din$target, levels = c("BigTarget", "SmallTarget"), labels = c("Big Target", "Small Target")), 
  vag = factor(din$vagueness, levels = c("Precise", "Vague"), labels = c("Crisp", "Vague")), 
  subit = factor(ifelse(din$pair %in% c(1,2,5,6), "Subitizable", "Not subitizable")),
  side = factor(din$side), 
  text = factor(din$Text),
  err = 1 - din$isCorrect, 
  rt_ms = din$rt,
  rt_log = log( din$rt ),
  rt_reciprocal = -1/din$rt)
# reciprocal is rate of slowing: "We multiplied reciprocal scores [1/RT] by -1 [-1/RT] to maintain the direction of effects compatible for the three variants, effectively converting speed [number of responses per ms] into 'rate of slowing' " - A linear mixed model analysis of masked repetition priming, Kliegl, Masson & Richter, VISUAL COGNITION,2010,18(5),655--681 (p.~662) 
```

### 2018-08-31 experiments/B_pilot_2/writeup/B_pilot_2.Rmd
consistent YAML

---
title: "B_pilot_2"
author: "Matt Green"
output:
  html_document:
    toc: yes
---

<!-- <style> -->
<!-- table, th, td { -->
<!--     border: 1px grey; -->
<!--     border-collapse: collapse; -->
<!--     padding:2px 5px 2px 5px -->
<!-- }   -->
<!-- </style> -->

<!-- no wrap table entries on their white space -->

<!-- <style> -->
<!-- table { -->
<!--   white-space: nowrap; -->
<!-- } -->
<!-- </style> -->

>>>>

---
title: "B_pilot_2"
author: "Matt Green"
output:
  html_document:
    toc: yes
    theme: default
    css: styles.css
---

### 2018-08-31 experiments/C_exp_1/writeup/C_exp_1.Rmd
did a bit more on e1, still needs stats numbers imported from Rmds
consistent YAML

---
title: "C_exp_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
    toc_float: false
---

@@

* For crisp verbal, we used Choose the square with the fewest dots. We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).

>>>>

---
title: "C_exp_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
    theme: default
    css: styles.css    
---

@@

* For crisp verbal, we used "Choose the square with the fewest dots". We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
